Fast, Scalable Phrase-Based SMT Decoding

### 2016-01-28 acl.2016/acl2016.tex
acl paper

There are two main optimization to the search that we shall investigate. Firstly, the search creates and destroy a large number of hypothesis objects in memory which puts a heavy burden on the operating system. Also, the speed of memory access is dependent on whether the data is in the CPU cache. We shall optimize the search algorithm to use memory pools and object pools, replacing the operating system's general purpose memory management with our own application-aware management. We shall also seek to re-use recently accessed information to increase likelihood of the data being in the CPU cache.

Secondly, we shall investigate different stack configurations other than coverage cardinality to see whether they can improve the speed / model score ratio.

@@

Load-on-demand \emph{'binary'} phrase-tables are often used for MT deployment due to their fast loading and fast querying speed, and because they can be used with large phrase-tables. We therefore focus on optimizing decoding speed with these phrase-tables, specifically the Probing PT.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
\# sentences  	& 800k 	& 200k \\
\# words 	& 5.8m 	& 5.9m \\ 
Avg words/sent	& 7.3	& 29.7 \\ \hline
\end{tabular}
\end{center}
\caption{Model sizes in GB}
\label{tab:test-sets}
\end{table}

>>>>

There are three main optimization to the search that we shall investigate. Firstly, the search creates and destroy a large number of hypothesis objects in memory which puts a heavy burden on the operating system. We shall optimize the search algorithm to use memory pools and object pools, replacing the operating system's general purpose memory management with our own application-aware management.

The speed of memory access is dependent on whether the data is in the CPU cache which is a constrained resource compared to memory size, typically 20MB in the latest processors. We shall seek to re-use recently accessed information to increase likelihood of the data being in the CPU cache.

In multiprocessor servers, the CPU cache is attached to each processor and each core. If a sentences is being decoded on one CPU is switched to another, the CPU cache on the new CPU must be repopulated, slowing down decoding. We will therefore investigate binding threads to specific cores.

Lastly, we shall investigate different stack configurations other than coverage cardinality to see whether they can improve the speed / model score ratio.

@@

Load-on-demand \emph{'binary'} phrase-tables are often used for MT deployment due to their fast loading and querying speed, and because they can be used with large phrase-tables. We therefore focus on optimizing decoding speed with these phrase-tables, specifically the Probing PT.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
\# sentences  	& 800k 	& 200k \\
\# words 	& 5.8m 	& 5.9m \\ 
Avg words/sent	& 7.3	& 29.7 \\ \hline
\end{tabular}
\end{center}
\caption{Test sets}
\label{tab:test-sets}
\end{table}
